### 2020-10-07 paper/natastron/si.tex

\subsubsection{Mode Linewidth ($\Gamma_{n,\ell}$)}
The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu. This can be expressed as an empirical relation \cite{davies+2014, appourchaux+2016, lund+2017}. However, this relation has six free parameters, none of which are directly relevant to this work. Instead of fitting this relation, we chose to employ a more flexible Gaussian Process \cite[GP]{rasmussen+williams2006} to act as a prior on the linewidths. This can be considered as us modelling the linewidths as correlated measurements, effectively loosely constraining how linewidth varies with frequency.

@@

To improve computational efficiency, we reduced the number of oscillation modes being fit in five targets. For 16 Cyg A \& B, KIC 7970740 and KIC 8478994, we excluded any modes with a Bayes Factor ($\ln(K)$) of less than 6, as reported in LEGACY \cite{kass+raftery1995,davies+2016,lund+2017}. For KIC 8478994, which is reported without a value for $\ln(K)$ in Kages, we only included modes of an overtone number that contained a detection for all of $\ell = (0, 1, 2)$, retaining 5 sets of higher signal-to-noise overtones. We do not expect this reduced scope to bias our results, although they may reduce the precision on our measured rotation rates.

@@

\bibliographystyle{naturemag}
\bibliography{library.bib} %

>>>>

\subsubsection{Mode Linewidth ($\Gamma_{n,\ell}$)}
The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu. This can be expressed as an empirical relation \cite{lund+2017, davies+2014, appourchaux+2016}. However, this relation has six free parameters, none of which are directly relevant to this work. Instead of fitting this relation, we chose to employ a more flexible Gaussian Process \cite[GP]{rasmussen+williams2006} to act as a prior on the linewidths. This can be considered as us modelling the linewidths as correlated measurements, effectively loosely constraining how linewidth varies with frequency.

@@

To improve computational efficiency, we reduced the number of oscillation modes being fit in five targets. For 16 Cyg A \& B, KIC 7970740 and KIC 8478994, we excluded any modes with a Bayes Factor ($\ln(K)$) of less than 6, as reported in LEGACY \cite{davies+2016,lund+2017,kass+raftery1995}. For KIC 8478994, which is reported without a value for $\ln(K)$ in Kages, we only included modes of an overtone number that contained a detection for all of $\ell = (0, 1, 2)$, retaining 5 sets of higher signal-to-noise overtones. We do not expect this reduced scope to bias our results, although they may reduce the precision on our measured rotation rates.

@@

\begin{thebibliography}{10}
	\expandafter\ifx\csname url\endcsname\relax
	\def\url#1{\texttt{#1}}\fi
	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
	\providecommand{\bibinfo}[2]{#2}
	\providecommand{\eprint}[2][]{\url{#2}}

	\bibitem{davies+2015}
	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
	\newblock \bibinfo{title}{Asteroseismic inference on rotation, gyrochronology
		and planetary system dynamics of 16 {{Cygni}}}.
	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
			Society}} \textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959}
	(\bibinfo{year}{2015}).

	\bibitem{chaplin+2011}
	\bibinfo{author}{Chaplin, W.~J.} \emph{et~al.}
	\newblock \bibinfo{title}{Ensemble {{Asteroseismology}} of {{Solar}}-{{Type
				Stars}} with the {{NASA Kepler Mission}}}.
	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{332}},
	\bibinfo{pages}{213} (\bibinfo{year}{2011}).

	\bibitem{harvey1985}
	\bibinfo{author}{Harvey, J.}
	\newblock \bibinfo{title}{High-{{Resolution Helioseismology}}}.
	\newblock \emph{\bibinfo{journal}{Future Missions in Solar, Heliospheric \&
			Space Plasma Physics}} \textbf{\bibinfo{volume}{235}}, \bibinfo{pages}{199}
	(\bibinfo{year}{1985}).

	\bibitem{chaplin+basu2017}
	\bibinfo{author}{Chaplin, W.~J.} \& \bibinfo{author}{Basu}.
	\newblock \emph{\bibinfo{title}{Asteroseismic {{Data Analysis}}:
			{{Foundations}} and {{Techniques}}}} (\bibinfo{publisher}{{Princeton
			University Press}}, \bibinfo{address}{{Princeton, New Jersey}},
	\bibinfo{year}{2017}), \bibinfo{edition}{1st} edn.

	\bibitem{davies+2016}
	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
	\newblock \bibinfo{title}{Oscillation frequencies for 35 {{Kepler}} solar-type
		planet-hosting stars using {{Bayesian}} techniques and machine learning}.
	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
			Society}} \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183}
	(\bibinfo{year}{2016}).

	\bibitem{lund+2017}
	\bibinfo{author}{Lund, M.~N.} \emph{et~al.}
	\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
		{{Kepler Asteroseismic LEGACY Sample}}. {{I}}. {{Oscillation Mode
				Parameters}}}.
	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
	\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{172} (\bibinfo{year}{2017}).

	\bibitem{tassoul1980}
	\bibinfo{author}{Tassoul, M.}
	\newblock \bibinfo{title}{Asymptotic approximations for stellar nonradial
		pulsations}.
	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
	\textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469} (\bibinfo{year}{1980}).

	\bibitem{vrard+2016}
	\bibinfo{author}{Vrard, M.}, \bibinfo{author}{Mosser, B.} \&
	\bibinfo{author}{Samadi, R.}
	\newblock \bibinfo{title}{Period spacings in red giants. {{II}}. {{Automated}}
		measurement}.
	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
	\textbf{\bibinfo{volume}{588}}, \bibinfo{pages}{A87} (\bibinfo{year}{2016}).

	\bibitem{hogg2012}
	\bibinfo{author}{Hogg, D.~W.}
	\newblock \bibinfo{title}{Data analysis recipes: {{Probability}} calculus for
		inference}.
	\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
	\bibinfo{pages}{arXiv:1205.4446} (\bibinfo{year}{2012}).

	\bibitem{hall+2019}
	\bibinfo{author}{Hall, O.~J.} \emph{et~al.}
	\newblock \bibinfo{title}{Testing asteroseismology with {{Gaia DR2}}:
		{{Hierarchical}} models of the {{Red Clump}}}.
	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
			Society}} \textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{3569--3585}
	(\bibinfo{year}{2019}).
	\newblock \eprint{1904.07919}.

	\bibitem{mazumdar+2014}
	\bibinfo{author}{Mazumdar, A.} \emph{et~al.}
	\newblock \bibinfo{title}{Measurement of acoustic glitches in solar-type stars
		from oscillation frequencies observed by {{Kepler}}}.
	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
	\textbf{\bibinfo{volume}{782}}, \bibinfo{pages}{18} (\bibinfo{year}{2014}).
	\newblock \eprint{1312.4907}.

	\bibitem{davies+2014}
	\bibinfo{author}{Davies, G.~R.}, \bibinfo{author}{Chaplin, W.~J.},
	\bibinfo{author}{Elsworth, Y.} \& \bibinfo{author}{Hale, S.~J.}
	\newblock \bibinfo{title}{{{BiSON}} data preparation: A correction for
		differential extinction and the weighted averaging of contemporaneous data}.
	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
			Society}} \textbf{\bibinfo{volume}{441}}, \bibinfo{pages}{3009--3017}
	(\bibinfo{year}{2014}).

	\bibitem{appourchaux+2016}
	\bibinfo{author}{Appourchaux, T.} \emph{et~al.}
	\newblock \bibinfo{title}{Oscillation mode linewidths and heights of 23
		main-sequence stars observed by {{{\emph{Kepler}}}}
		{\emph{(}}{{{\emph{Corrigendum}}}}{\emph{)}}}.
	\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
	\textbf{\bibinfo{volume}{595}}, \bibinfo{pages}{C2} (\bibinfo{year}{2016}).

	\bibitem{rasmussen+williams2006}
	\bibinfo{author}{Rasmussen, C.~E.} \& \bibinfo{author}{Williams, C. K.~I.}
	\newblock \emph{\bibinfo{title}{Gaussian Processes for Machine Learning}}.
	\newblock Adaptive Computation and Machine Learning (\bibinfo{publisher}{{MIT
			Press}}, \bibinfo{address}{{Cambridge, Mass}}, \bibinfo{year}{2006}).

	\bibitem{toutain+appourchaux1994}
	\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Appourchaux, T.}
	\newblock \bibinfo{title}{Maximum likelihood estimators: {{An}} application to
		the estimation of the precision of helioseismic measurements}.
	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
	\textbf{\bibinfo{volume}{289}}, \bibinfo{pages}{649--658}
	(\bibinfo{year}{1994}).

	\bibitem{gizon+solanki2003}
	\bibinfo{author}{Gizon, L.} \& \bibinfo{author}{Solanki, S.~K.}
	\newblock \bibinfo{title}{Determining the {{Inclination}} of the {{Rotation
				Axis}} of a {{Sun}}-like {{Star}}}.
	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
	\textbf{\bibinfo{volume}{589}}, \bibinfo{pages}{1009} (\bibinfo{year}{2003}).

	\bibitem{handberg+campante2011}
	\bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Campante, T.~L.}
	\newblock \bibinfo{title}{Bayesian peak-bagging of solar-like oscillators using
		{{MCMC}}: A comprehensive guide}.
	\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
	\textbf{\bibinfo{volume}{527}}, \bibinfo{pages}{A56} (\bibinfo{year}{2011}).

	\bibitem{woodard1984}
	\bibinfo{author}{Woodard, M.~F.}
	\newblock \emph{\bibinfo{title}{Short-{{Period Oscillations}} in the {{Total
					Solar Irradiance}}.}}
	\newblock Ph.D. thesis (\bibinfo{year}{1984}).

	\bibitem{anderson+1990}
	\bibinfo{author}{Anderson, E.~R.}, \bibinfo{author}{Duvall, T.~L.} \&
	\bibinfo{author}{Jefferies, S.~M.}
	\newblock \bibinfo{title}{Modeling of {{Solar Oscillation Power Spectra}}}.
	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
	\textbf{\bibinfo{volume}{364}}, \bibinfo{pages}{699} (\bibinfo{year}{1990}).

	\bibitem{vanhoey+2013}
	\bibinfo{author}{Van~Hoey, S.}, \bibinfo{author}{{van der Kwast}, J.},
	\bibinfo{author}{Nopens, I.} \& \bibinfo{author}{Seuntjens, P.}
	\newblock \bibinfo{title}{Python package for model {{STructure ANalysis}}
		({{pySTAN}})}.
	\newblock \emph{\bibinfo{journal}{EGU General Assembly Conference Abstracts}}
	\textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{EGU2013--10059}
	(\bibinfo{year}{2013}).

	\bibitem{salvatier+2016}
	\bibinfo{author}{Salvatier, J.}, \bibinfo{author}{Wiecki, T.~V.} \&
	\bibinfo{author}{Fonnesbeck, C.}
	\newblock \bibinfo{title}{Probabilistic programming in {{Python}} using
		{{PyMC3}}}.
	\newblock \emph{\bibinfo{journal}{PeerJ Computer Science}}
	\textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{e55} (\bibinfo{year}{2016}).

	\bibitem{gelman2006}
	\bibinfo{author}{Gelman, A.}
	\newblock \bibinfo{title}{Prior distributions for variance parameters in
		hierarchical models (comment on article by {{Browne}} and {{Draper}})}.
	\newblock \emph{\bibinfo{journal}{Bayesian Analysis}}
	\textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{515--534}
	(\bibinfo{year}{2006}).

	\bibitem{ballot+2006}
	\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Garcia, R.~A.} \&
	\bibinfo{author}{Lambert, P.}
	\newblock \bibinfo{title}{Rotation speed and stellar axis inclination from p
		modes: How {{CoRoT}} would see other suns}.
	\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
			Society}} \textbf{\bibinfo{volume}{369}}, \bibinfo{pages}{1281--1286}
	(\bibinfo{year}{2006}).

	\bibitem{ballot+2008a}
	\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Appourchaux, T.},
	\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Guittet, M.}
	\newblock \bibinfo{title}{On deriving p-mode parameters for inclined solar-like
		stars}.
	\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
	\textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{867--875}
	(\bibinfo{year}{2008}).
	\newblock \eprint{0803.0885}.

	\bibitem{kass+raftery1995}
	\bibinfo{author}{Kass, R.~E.} \& \bibinfo{author}{Raftery, A.~E.}
	\newblock \bibinfo{title}{Bayes {{Factors}}}.
	\newblock \emph{\bibinfo{journal}{Journal of the American Statistical
			Association}} \textbf{\bibinfo{volume}{90}}, \bibinfo{pages}{773--795}
	(\bibinfo{year}{1995}).

\end{thebibliography}
